Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-08-13 demystify.tex
updates

Moreover, having bad grades in relevant courses, e.g., Math and CS, can be a \red{red flag}.
Adcom members often scan through transcripts looking for C and lower grades in Math and CS courses and might raise concerns if they see several of them.
Note that bad grades in non-relevant courses, e.g., e.g., about politics or history, are not as concerning.

A common question is whether you should be concern and explain bad grades in relevant courses in your SOP.  If you have just a few, then they do not matter much, so don't spend much time explaining them (let's face it, many of us, including faculty, have bad grades in some courses, including relevant ones). But if you have many bad grades for an entire semester or year due to some specific reasons, then you may be you should explain them in your SOP.

\section{Standard Tests (GRE, IELTS, etc), Online Courses, and Certificates}\label{sec:standard-tests}

@@

\paragraph{Not getting interviews} While it is generally good to get an interview, not getting one \emph{does not} mean you're out.  Many programs do not have the tradition of interviewing applicants. For example, at Mason, most admitted students with TA (\autoref{sec:ta}) do not go through interviews.

@@

\paragraph{What else?} Make a decision, accept, reject, or defer the offers  (\autoref{sec:accept-postpone-decline}). Ask to meet with potential advisers (e.g., through Open House or separately) and even their students. Ask about computer equipment and software, office space, and other resources; in many cases these will be provided for free by your adviser or department (\autoref{sec:buying-equipment}).

@@

\paragraph{Should I ask for feedback?}
No, don't bother.  You will likely not get any useful feedback.  We are not willing to reveal your evaluation results or give you advice on how to improve your profile. So it is best to just move on.  If you really want feedback, ask your professors, collaborators, ref writers, or those who have previously applied.

>>>>

Moreover, having bad grades in relevant courses, e.g., Math and CS, can be a \red{red flag}.
Adcom members often scan through transcripts (\autoref{sec:ievaluate}) looking for C and lower grades in Math and CS courses and might raise concerns if they see several of them.
Note that bad grades in non-relevant courses, e.g., e.g., about politics or history, are not as concerning.

A common question is whether you should be concern and explain bad grades in relevant courses in your SOP.  If you have just a few, then they do not matter much, so don't spend much time explaining them (many adcom reviewers, like myself, have bad grades in relevent courses!). But if you have many bad grades for an entire semester or year due to some specific reasons, then you may be you should explain them in your SOP.

\section{Standard Tests (e.g., GRE and IELTS), Online Courses, and Certificates}\label{sec:standard-tests}

@@

\subsection{Not Getting Interviews} While it is generally good to get an interview, not getting one \emph{does not} mean you're out.  Many programs do not have the tradition of interviewing applicants. For example, at Mason, most admitted students with TA (\autoref{sec:ta}) do not go through interviews.

@@

\paragraph{What next?} Make a decision, accept, reject, or defer the offers  (\autoref{sec:accept-postpone-decline}). Ask to meet with potential advisers (e.g., through Open House or separately) and even their students. Ask about computer equipment and software, office space, and other resources; in many cases these will be provided for free by your adviser or department (\autoref{sec:buying-equipment}).

@@

\paragraph{Should I ask for feedback?}
No, don't bother.  You will likely not get any useful feedback.  We are not willing (allowed) to reveal your evaluation results or give you advice on how to improve your profile. So just move on.  If you really want feedback, ask your professors, collaborators, ref writers, or those who have previously applied.
